Characterization of integrated crop-livestock-forest system in Brazil

### 2022-07-27 iclfs_review/lit_review.qmd
Update search strings.

Scopus: TITLE-ABS-KEY(iclf OR iclfs OR crop-livestock-forestry OR crop-livestock-forest OR agrosilvipastoral OR ilpf OR lavoura-pecuária-floresta OR agrosilvipastoril)

Embrapa: (ICLF) OR (iclfs) OR (crop-livestock-forestry) OR (crop-livestock-forest) OR (agrosilvipastoral) OR (ilpf) OR (lavoura-pecuária-floresta) OR (agrosilvipastoril)

>>>>

Scopus: TITLE-ABS-KEY(iclf OR iclfs OR crop-livestock-forestry OR crop-livestock-forest OR agrosilvipastoral OR ilpf OR lavoura-pecuária-floresta OR agrosilvipastoril) AND PUBYEAR > 1999

Embrapa: ((ICLF) OR (iclfs) OR (crop-livestock-forestry) OR (crop-livestock-forest) OR (agrosilvipastoral) OR (ilpf) OR (lavoura-pecuária-floresta) OR (agrosilvipastoril)) AND (ano-publicacao:[2000 TO *]) AND (tipo-material-sigla:"PC" OR tipo-material-sigla:"AP" OR tipo-material-sigla:"NC" OR tipo-material-sigla:"RT") AND (idioma:"Inglês" OR idioma:"Português")
